Simulating High-Dimensional Multivariate Data

### 2021-02-25 050-examples.Rmd

```{r ch050-LoadLib, include=FALSE, cache=FALSE}
box::use(
  dplyr[...],
  ggplot2[...],
  patchwork[...],
  bigsimr[...],
  knitr[include_graphics]
)
load("data/example_brca.rda")
load("data/example_genes.rda")

@@

set.seed(10142020)
```

@@

```{r ch050-figBRCA, out.width='80%', fig.cap="Simulated random vectors from a multivariate negative binomial replicate the estimated structure from an RNA-seq data set. The dashed red lines indicated equality between estimated parameters from simulated data (vertical axes) and the specified target parameters (horizontal axes)."}
include_graphics('fig/ch050-figBRCA.png')
```

>>>>

```{r ch050-LoadLib, include=FALSE, cache=FALSE}
devtools::load_all()
library(tidyverse)
library(patchwork)
library(bigsimr)

@@

cores <- as.integer(parallel::detectCores() - 1)
set.seed(10142020)
```

@@

```{r ch050-figBRCA, out.width='80%', fig.cap="Simulated random vectors from a multivariate negative binomial replicate the estimated structure from an RNA-seq data set. The dashed red lines indicated equality between estimated parameters from simulated data (vertical axes) and the specified target parameters (horizontal axes)."}
knitr::include_graphics('fig/ch050-figBRCA.png')
```
